\documentclass[conference]{IEEEtran}

% === 1. LES PAQUETS (Les outils de base) ===
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}

% === 2. LE DOSSIER DES IMAGES ===
\graphicspath{{../Dossier_graphiques/Dashboard_Ultime/}}

\begin{document}

% === 3. EN-TÊTE DU DOCUMENT ===
\title{Multimodal Data Fusion in IoMT For Early Disease Detection using Deep Learning with Generated Data}

\author{
    \IEEEauthorblockN{Doralie Dorcal, Olivier Tram}
    \IEEEauthorblockN{Jiahui Xiang, Osman Salem, Ahmed Mehaoua}
    \IEEEauthorblockA{
        \textit{Université Paris Cité}, Paris, France \\
        student's mail : \{firstname.lastname\}@etu.u-paris.fr \\
        teacher's mail : \{firstname.lastname\}@u-paris.fr
    }
}

\maketitle

% === 4. LE CORPS DU DOCUMENT ===

\input{Sections/0-Abstract.tex}

\input{Sections/1-Introduction.tex}

\input{Sections/2-Related_Work.tex}

\input{Sections/3-Proposed_Approach.tex}

\input{Sections/4-Experimental_Results.tex}

\input{Sections/5-Conclusion.tex}

% === 5. BIBLIOGRAPHIE ===

\begin{thebibliography}{00}

\bibitem{choi2017}
E. Choi, S. Biswal, B. Malin, J. Duke, W. F. Stewart, and J. Sun, ``Generating Multi-label Discrete Patient Records using Generative Adversarial Networks,'' in \textit{Machine Learning for Healthcare Conference}, PMLR, pp. 286-305, 2017.

\bibitem{baltrusaitis2018}
T. Baltrušaitis, C. Ahuja, and L.-P. Morency, ``Multimodal Machine Learning: A Survey and Taxonomy,'' \textit{IEEE Transactions on Pattern Analysis and Machine Intelligence}, vol. 41, no. 2, pp. 423-443, 2019.

\bibitem{rahmani2018}
A. M. Rahmani et al., ``Exploiting smart e-Health gateways at the edge of healthcare Internet-of-Things: A fog computing approach,'' \textit{Future Generation Computer Systems}, vol. 78, pp. 641-658, 2018.

\bibitem{gorishniy2021}
Y. Gorishniy, I. Rubachev, V. Khrulkov, and A. Babenko, ``Revisiting Deep Learning Models for Tabular Data,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 34, pp. 18932-18943, 2021.

\bibitem{lundberg2017}
S. M. Lundberg and S.-I. Lee, ``A Unified Approach to Interpreting Model Predictions,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, vol. 30, 2017.

\end{thebibliography}

\end{document}

\end{document}